Color- and piece-blind chess

### 2019-03-08 trunk/chess/papers/blind.tex
Good progress on the unblinder part

What better way for humans to impress each other with their brains,
especially in movies, than to play chess---and to shout dramatically
CHECKMATE! upon surprise-checkmating their opponent? Well, one way is
to play chess while disadvantaged somehow, for example, by punching
each other in the face repeatedly during the game to impair brain
function (see Chess Boxing~\cite{chessboxing}). Another common
distraction is to play a multitude of games against many opponents at
the same time, in a so-called ``simultaneous exhibition.'' The idea is
that this is more challenging because of the need to maintain mental
state for so many games at once, whereas your opponents only need to
maintain state for one game. In truth, simultaneous exhibitions easily
fall to a ``man-in-the-middle attack.'' If the purported genius simply
creates a bipartite matching of the games played with the white pieces
and the games played with black, he can mechanically forward moves
between these pairs of boards. This requires only constant state (see
next section) per pair of games, and guarantees an even score for the
exhibition. So that's not very impressive.

Another disadvantage that humans sometimes use to impress each other
is a blindfold (worn over the eyes). In this predicament they only
hear the opponent announce moves and must keep the position on the
board in their mind's eye, both for the sake of remembering it and
while exploring potential moves.
% This is effective, since although the .
Disadvantages can be combined, such as in the final scene of the 1988
documentary {\it Bloodsport} where Jean Claude van Damme is blinded by
an illicit foreign substance during the final martial art
battle.\footnote{JCVD does not play chess on camera, but it is implied
  that he is also holding a simultaneous exhibition between rounds in
  a different room of the underground Hong Kong illegal karate
  complex.}

@@

There are $n/2$ pairs, with two bits for the state, no more\footnote{
  There are only 1792 pairs of squares between which pieces can ever
  move (Section~\ref{sec:legalmove}), so $11+2$ bits suffices, with
  some added complexity.} than $\log_2(64 * 64 * 4) = 14$ bits for
each move (source square, destination square, and 2 bits to
distinguish promotion to queen, rook, bishop, or knight). However, we
also need to store the matching of $G_w$ to $G_b$; this can be done
with a pair of indices (or e.g. memory addresses) but unfortunately,
this requires $\log_2(n)$ bits to represent. So overall this approach
requires $O(n \log(n))$ space to play a simultaneous exhibition of $n$
games.

@@

Although this is more involved than the previous approach, and may
take exponential time, it allows us to play against $n$ simultaneous
opponents using $O(n)$ space!\footnote{ 
%
If the games in the exhibition were presented to us in some way that
allowed us to visit them in the same order multiple times, we could
perhaps get away with {\em only} the random pool? XXX }
%
The actual space used per game is primarily the representation of
a chess position, plus a few bits for bookkeeping. So, representing
boards compactly gives us a way to increase the number of simultaneous
games we can play for a given storage size.

Mainly, we need to store the pieces and their locations. There are a
few other bits, like whose turn it is (1 bit), whether each player can
still castle king- and queen-side (4 bits), and whether and where an
en passant capture is possible (4 bits).\footnote{
%
Technically, we need to store a lot of additional information with the
board in order to completely implement the rules of
chess.\cite{fiderules} The trickiest of these involve the rules for
draw by repetition, which make reference to the history of the game
(See Footnote~1 in {\it Survival in chessland}\cite{survival} and seem
to require storing all previous board states. Fortunately, if we are
being this picky, then we also know that the length of a chess game is
bounded by a constant: Rule 9.6.2 ends the game in a draw if both
players have made 75 moves without a pawn move or
capture,\footnotemark\ so it suffices to store the $75*2$ most recent
(half-)moves. This sucks so most people don't do it (for example, FEN
notation only gives the number of such moves, and so cannot implement
the draw by repetition). On the other hand, if we insist, then this
may give us a simpler route to a constant-space exhibition, since the
$B \stepsto{m} B'$ relation is probably reversible with such
information.}\footnotetext{These are two types of moves that make it impossible
  to formally repeat a position that preceded them. Castling also has
  this property, but doesn't count because it is a ``secret move.''}

With 64 squares, six pieces for each of the two sides, plus the empty
square, a straightforward representation of the board uses $64*4=256$
bits. The Thursd'z Institute considered more compact
representations\cite{representations}; one nice choice works as follows:

Start with a single 64-bit mask which indicates, for each square on
the board, whether it contains any piece. Note that there can only be
up to 32 pieces on the board. To tell what these pieces are, we then
follow with 32 four-bit records; these indicate the piece's color and
type.\footnote{(Since only 32 of the 64 bits can be set, you could do
  slightly better by representing $\binom{60}{32}$ in $\sim 61$ bits.
  When fewer than 32 squares are occupied, we can use a record
  containing e.g. a third king (otherwise impossible) to indicate that
  we should ignore the remaining bits. However, this gets vastly more
  complicated for only 3 bits of savings.)} 
%
With the 9 bits of extra state above, this totals $64+32*4+9=201$
bits. There is some slack in the representation, because there are
only 12 actual possibilities for a piece but we can indicate 16 with 4
bits. It is great to abuse this slack to save bits; for example, we
can store a new type of rook that is still able to castle (it can only
be in the corners and thus also indicates its own color), eliminating
the 4 castling bits. We can similarly introduce an en-passantable
pawn, saving the 4 bits of en passant state; this piece can only be in
ranks 4 or 5, so it also indicates its color. We can also have a
``king whose turn it is'' for each side, saving the side-to-move bit.
This totals a nice round $64+32*4=192$ bits.\footnote{ Since this is
  SIGBOVIK, I am freed from the burden of comparing related work. I
  did however read the rather bad Wikipedia article on the
  topic\cite{wikipediaboard} which describes a Huffman-based encoding
  that uses a ``maximum of 204 bits, and often much less.'' This also
  includes a 7-bit 50-move counter (but you really need to implement a
  75-move counter; 50 moves only allow a player to {\em claim} a draw)
  so should be compared as $197$ bits. But the article also contains
  many bugs, like the misconception that there can only be four total
  rooks (pawns are allowed to promote to rook). So the approach
  described here is both {\em more efficient} and {\em more correct}.}
%
This would allow approximately an 11 billion-game simultaneous
exhibition in RAM on my desktop computer.

@@

So this is kind of like blindfold chess ... XXX

% 
% % make -j eval-unblinder.exe && ./eval-unblinder.exe net.val
% .!Evaluating model net.val...
% Loaded 50000 positions in 122.59s
% Loaded model in 0.10s
% Ran eval in 2.04s
% Reading [net.val]
% net.val: 4 layers.
% net.val: num nodes: 64 1024 12288 567 837
% net.val: indices per node/fns: 49 LEAKY_RELU 36 LEAKY_RELU 127 LEAKY_RELU 78 LEAKY_RELU
% Read from net.val.
% Invert index:
% Check it:
% ModelInfo [339885 rounds, 223224128 examples]
% Over 50000 positions:
%   9584 exactly correct (19.17%)
%   161166 piece mistakes (3.22/pos)
%   1630 castling mistakes (0.03/pos)
%   19014 move mistakes (0.38/pos)
%   181810 total mistakes (3.64/pos)
% 
% % $ make -j eval-unblinder.exe && ./eval-unblinder.exe net-before-vacuum.val
% make: 'eval-unblinder.exe' is up to date.
% Evaluating model net-before-vacuum.val...
% Loaded 50000 positions in 118.80s
% Loaded model in 3.99s
% Ran eval in 332.10s
% Reading [net-before-vacuum.val]
% net-before-vacuum.val: 4 layers.
% net-before-vacuum.val: num nodes: 64 1024 12288 567 837
% net-before-vacuum.val: indices per node/fns: 64 LEAKY_RELU 1024 LEAKY_RELU 12288 LEAKY_RELU 567 LEAKY_RELU
% Read from net-before-vacuum.val.
% Invert index:
% Check it:
% ModelInfo [146999 rounds, 9407936 examples]
% Over 50000 positions:
%   10601 exactly correct (21.20%)
%   156052 piece mistakes (3.12/pos)
%   1542 castling mistakes (0.03/pos)
%   18818 move mistakes (0.38/pos)
%   176412 total mistakes (3.53/pos)
% 
% 
% 
% without concurrent processes:
% net.val: 1.61s  (something like 1035/sec/core)
% net-before-vacuum: 229.85s (something like 7/sec/core)
% 
% 
% single_kings net.val:
% Over 50000 positions:
%   9642 exactly correct (19.28%)
%   162804 piece mistakes (3.26/pos)
%   1633 castling mistakes (0.03/pos)
%   19014 move mistakes (0.38/pos)
%   183451 total mistakes (3.67/pos)
% 
% It's actually kind of heartening that it performs worse with this approach,
% though we are more likely to get the whole board correct.
% 
% (cite #kingme)
%

% all bits set to 1 (with single_kings)
% (without single_kings, only difference is that the bottom right becomes a
% rook; no white queen)
\includegraphics[width=0.9 \linewidth]{blind-allon}

>>>>

What better way for humans to impress each other with their brains,
especially in movies, than to play chess---and to shout dramatically
CHECKMATE! upon surprise-checkmating their opponent? Well, one way is
to play chess while disadvantaged somehow, for example, by punching
each other in the face repeatedly during the game to impair brain
function (see Chess Boxing~\cite{wikipediachessboxing}). Another common
distraction is to play a multitude of games against many opponents at
the same time, in a so-called ``simultaneous exhibition.'' The idea is
that this is more challenging because of the need to maintain mental
state for so many games at once, whereas your opponents only need to
maintain state for one game. In truth, simultaneous exhibitions easily
fall to a ``man-in-the-middle attack.'' If the purported genius simply
creates a bipartite matching of the games played with the white pieces
and the games played with black, he can mechanically forward moves
between these pairs of boards. This requires only constant state (see
next section) per pair of games, and guarantees an even score for the
exhibition. So that's not very impressive.

Another disadvantage that humans sometimes use to impress each other
is a blindfold (worn over the eyes). In this predicament they only
hear the opponent announce moves and must keep the position on the
board in their mind's eye, both for the sake of remembering it and
while exploring potential moves.
% This is effective, since although the .
Disadvantages can be combined, such as in the final scene of the 1988
documentary {\it Bloodsport} where Jean Claude van Damme is blinded by
an illicit foreign substance during the final martial art
battle.\footnote{JCVD does not play chess on camera, but it is implied
  that he is also holding a simultaneous exhibition between rounds in
  a different room of the underground Hong Kong illegal karate
  complex.}
% Note: blindfold simuls are banned in russia as a health hazard!?

@@

There are $n/2$ pairs, with two bits for the state, no more\footnote{
  There are only 1792 pairs of squares between which pieces can ever
  move (Section~\ref{sec:legalmove}), so $11+2$ bits suffices, with
  some added complexity.} than $\log_2(64 \times 64 \times 4) = 14$ bits for
each move (source square, destination square, and 2 bits to
distinguish promotion to queen, rook, bishop, or knight). However, we
also need to store the matching of $G_w$ to $G_b$; this can be done
with a pair of indices (or e.g. memory addresses) but unfortunately,
this requires $\log_2(n)$ bits to represent. So overall this approach
requires $O(n \log(n))$ space to play a simultaneous exhibition of $n$
games.

@@

Although this is more involved than the previous approach, and may
take exponential time, it allows us to play against $n$ simultaneous
opponents using $O(n)$ space!\footnote{ 
%
If the games in the exhibition were presented to us in some way that
allowed us to visit them in the same order multiple times, we could
perhaps get away with {\em only} the random pool? XXX }

\subsection{Board representations} \label{sec:representation}

The actual space used per game is primarily the representation of
a chess position, plus a few bits for bookkeeping. So, representing
boards compactly gives us a way to increase the number of simultaneous
games we can play for a given storage size.

Mainly, we need to store the pieces and their locations. There are a
few other bits, like whose turn it is (1 bit), whether each player can
still castle king- and queen-side (4 bits), and whether and where an
en passant capture is possible (4 bits).\footnote{
%
Technically, we need to store a lot of additional information with the
board in order to completely implement the rules of
chess.\cite{fiderules} The trickiest of these involve the rules for
draw by repetition, which make reference to the history of the game
(See Footnote~1 in {\it Survival in chessland}\cite{survival} and seem
to require storing all previous board states. Fortunately, if we are
being this picky, then we also know that the length of a chess game is
bounded by a constant: Rule 9.6.2 ends the game in a draw if both
players have made 75 moves without a pawn move or
capture,\footnotemark\ so it suffices to store the $75\times 2$ most recent
(half-)moves. This sucks so most people don't do it (for example, FEN
notation only gives the number of such moves, and so cannot implement
the draw by repetition). On the other hand, if we insist, then this
may give us a simpler route to a constant-space exhibition, since the
$B \stepsto{m} B'$ relation is probably reversible with such
information.}\footnotetext{These are two types of moves that make it impossible
  to formally repeat a position that preceded them. Castling also has
  this property, but doesn't count because it is a ``secret move.''}

With 64 squares, six pieces for each of the two sides, plus the empty
square, a straightforward representation of the board uses $64 \times 4=256$
bits. The Thursd'z Institute considered more compact
representations\cite{representations}; one nice choice works as follows:

Start with a single 64-bit mask which indicates, for each square on
the board, whether it contains any piece. Note that there can only be
up to 32 pieces on the board. To tell what these pieces are, we then
follow with 32 four-bit records; these indicate the piece's color and
type.\footnote{(Since only 32 of the 64 bits can be set, you could do
  slightly better by representing $\binom{60}{32}$ in $\sim 61$ bits.
  When fewer than 32 squares are occupied, we can use a record
  containing e.g. a third king (otherwise impossible) to indicate that
  we should ignore the remaining bits. However, this gets vastly more
  complicated for only 3 bits of savings.)} 
%
With the 9 bits of extra state above, this totals $64+32 \ times 4+9=201$
bits. There is some slack in the representation, because there are
only 12 actual possibilities for a piece but we can indicate 16 with 4
bits. It is great to abuse this slack to save bits; for example, we
can store a new type of rook that is still able to castle (it can only
be in the corners and thus also indicates its own color), eliminating
the 4 castling bits. We can similarly introduce an en-passantable
pawn, saving the 4 bits of en passant state; this piece can only be in
ranks 4 or 5, so it also indicates its color. We can also have a
``king whose turn it is'' for each side, saving the side-to-move bit.
This totals a nice round $64+32 \times 4=192$ bits.\footnote{ Since this is
  SIGBOVIK, I am freed from the burden of comparing related work. I
  did however read the rather bad Wikipedia article on the
  topic\cite{wikipediaboard} which describes a Huffman-based encoding
  that uses a ``maximum of 204 bits, and often much less.'' This also
  includes a 7-bit 50-move counter (but you really need to implement a
  75-move counter; 50 moves only allow a player to {\em claim} a draw)
  so should be compared as $197$ bits. But the article also contains
  many bugs, like the misconception that there can only be four total
  rooks (pawns are allowed to promote to rook). So the approach
  described here is both {\em more efficient} and {\em more correct}.}
%
This would allow approximately an 11 billion-game simultaneous
exhibition in RAM on my desktop computer.

@@

\section{Color- and piece-blind chess}

So this is kind of like blindfold chess, but for computers! Instead of
being blind to the board, and only relying on our memory (trivial for
computers), we'll only be able to see where pieces are positioned on
the board, but not what type or color they are. Of course, we also
have to prohibit the computer from simply remembering the board, so
the algorithm must be stateless. Specifically, we want a function
\[
  {\tt makemove} : {\tt uint64} \rightarrow {\tt move list}
\]
that makes a move from a single board position, represented just as 64
bits. This is a single move; the move list represents our preference
for the move to make in descending order, and we commit to the first
move that is actually legal. It does not work well to insist that the
function return a single move, as it will often be the case that the
board is misinterpreted and a move is in fact illegal; forcing
forfeit\footnote{FIDE rules state that the {\em second} attempt at an
  illegal move results in forfeit (7.5.5).} would mean that almost all
games end in forfeit, which is boring. On the other hand, allowing the
function to try again upon learning a move is illegal would allow it
to interactively ``interrogate'' the board state
somewhat.\footnote{Similar to Kriegspiel~\cite{wikipediakriegspiel}, although
  in that game at least one's own pieces are known!} This seems
counter to the spirit of color- and piece-blind chess, so we instead
require the function to rank all moves ahead of time.

\section{Unblinding the board}

I went about this by building a function that ``unblinds'' a board; it
has type
\[
{\tt unblind} : {\tt uint64} \rightarrow {\tt position}
\]

This function is natural for machine learning. It is easy to generate
copious training data from actual games by simply blinding positions
into their corresponding 64-bit numbers; I just randomly sampled 100
million positions from Feburary~2017 on lichess.org.

I repurposed the custom neural network code from my seminal paper {\it
  Red i removal with artificial retinal networks}~\cite{redi} after
discovering that artificial retinal networks are actually {\em
  isomorphic} to neural networks. The main advantage of this code is
that it allows for sparse networks, but the real reason to use it is
that I would rather spend dozens of hours debugging my own code, pay a
larger electric bill, and get worse results in the end, than to spend
a short while trying to get someone else's probably-very-good neural
network training package to compile.

The structure of the network is as follows. The input layer is 64
nodes, one for each of the 64 bits, with each node set to either {\tt
  1.0f} or {\tt 0.0f}. Three hidden layers of size 1024, 12288, and 567
do the neural magic. The output layer is 837 nodes; the bulk of which
is a ``one-hot'' representation of the predictions for the 64 squares,
each with 13 possible contents (black or white, six pieces, or empty).
This is $64 \times 13 = 832$ nodes. Then four nodes to predict the
four castling bits, and one to predict the current side to move. This
model does not predict the possibility for {\em en passant} capture,
nor move counters or position repetition. This will not be its main
source of disadvantage!

I trained the network in two phases, first starting with a densely
connected one (model size 160 MB), and then after I get fed up with
how slow training was, a ``vacuumed'' version of the network where I
removed edges with low absolute weights (model size 5 MB) to continue
training. Removing edges based on an absolute weight threshold is
very unprincipled (since a downstream edge can magnify a contribution
arbitrarily) but I did it anyway.

Everything was trained on a single GPU, though a fairly decent one in
2018, the EVGA GeForce GTX 1080 FTW (really), using OpenCL. Biases
were initialized to $0$ and weights with a Gaussian of mean $0$ and
standard deviation $0.025$. In the first phase, there were 64 examples
per round, and after vacuuming, 2048. The round learning rate
$\alpha_r$ started at $0.1$ and descended linearly to $0.002$ over
500,000 rounds; and the learning rate when updating weights (for each
example) $\alpha$ is $\alpha_r / \verb+examples_per_round+$. In no way
am I recommending these parameters. Fiddling with the parameters to
make it do its black magic or alternately carom off to a sea of NaNs
or zeroes is for sure the worst part of neural networks. In fact, I
initially started with the classical sigmoid transfer function, but
``upgraded'' to the ``leaky rectified linear'' function
%
$$((potential < 0.0f) ? potential * 0.01f : potential)$$
%
after getting fed up with sigmoid weights caroming off (see
``vanishing gradient problem'' and/or ``exploding gradient problem'').
The final model was trained over 339,885 rounds on 223 million
examples. It did not appear to show signs of improving for
several days before I terminated it.

\subsection{Statistical evaluation}

The unblinding component can be evaluated on its own, by running
it on examples sampled independently of the training set. Over
50,000 examples, these were the results:

9,584 predicted boards were exactly correct (19.17\%). There were a
total of 161,166 piece mistakes, which is an average of 3.22 per
board. This is wherever we predict a square's contents incorrectly.
There were only 1630 castling status mistakes, an average of 0.03 per
board (there can be up to four mistakes per board). This is probably
because when the king and rook are in their starting squares, castling
is almost always still allowed. In 19,014 boards, we mispredicted
whose move it is (38\%). This appears to be the most difficult thing
to predict, which is not surprising.\footnote{ Prior to ``vacuuming'',
  the 160 MB network actually performed slightly better than the final
  5 MB network, with 21.20\% of boards exactly correct, and an average
  of 3.12 mistakes per board. This suggests that the model may only be
  doing a limited amount of generalization, instead mostly memorizing
  board positions. Representing the 223 million examples seen exactly
  (using our best board representation described in
  Section~\ref{sec:representation}) would take 42.8 GB, so at 5 MB at
  least the data is represented compactly, if also rather lossily.}

\subsection{Subjective evaluation}

The unblinder {\em must} make mistakes since the 64-bit representation
is ambiguous. Subjectively, the unblinder makes reasonable mistakes.
It is excellent at common openings, usually getting these exactly
correct. On the other hand, it is fairly bad at sparse endgames, where
it is difficult to tell a pawn from a rook from a king. It is terrible
at unlikely positions that can be confused for likely ones. If you are
playing against it and know how it works, it is easy to trick it by
doing something like capturing one of its starting-position pawns with
your queen; nobody does this in real games (because the queen can be
immediately recaptured), so the square is predicted as a pawn and the
queen ``disappears'' to the unblinder (Figure~\ref{fig:trick}). Having
an invisible queen in your camp is of course very dangerous. Resolving
ambiguities in favor of more likely positions is the right thing for
the model to do, so this is just an inherent flaw with the
decomposition of the problem. There are some ways we can account for
this (Section~\ref{sec:using}). % XXX make sure I did this work

\begin{figure}[ht]
XXX actual example
\caption{The white queen ``disappears'' after QxWhatever, because
  unblinding predicts it to be one of black's own pawns, which is far
  more likely in that square.} \label{fig:trick}
\end{figure}

A few things are distinctly disappointing about its performance. Even
outside of ``likely'' positions, it usually predicts that pieces on
black's side of the board are black, and vice versa
(Figure~\ref{fig:allon}). This makes sense, but suggests serious
limitation on using the prediction to play chess. Less forgivably, it
sometimes predicts more than one king per side (or zero), which is
always wrong. Actually, an early version had this problem in spades,
usually frequently predicting two or three kings. Upon debugging, I
had simply made the noob mistake of printing both King and Knight with
the letter ``K.'' Ha! It often predicts the ``wrong'' number of
bishops (etc.), or places them on the same color. This is technically
possible through promotion, but usually a bad guess, since promotion
is relatively rare, and moreso promotion to a piece other than a
queen. An approach that might handle this better (but may have
different downsides) would be instead to predict the ``fates'' of the
32 initial pieces. The fate of a pawn can include promotion, but no
other pieces can. This would {\em require} that the model only predict
a single location for each king, among other things. However, this
would require a much larger output layer (32 pieces can move to 64
squares, plus promotion) and it is not always clear how to interpret
its value into a position (for example, if two pieces are predicted
strongly to be on the same square).

\begin{figure}[ht]
\includegraphics[width=0.9 \linewidth]{blind-allon}
\caption{What the model predicts (in single-king mode;
  Section~\ref{sec:using}) for {\tt 0xFFFFFFFFFFFFFFFF}, the board
  with all bits set. This is an impossible position, but it gives some
  idea of the model's biases for each square. Notably, most of the pieces
  on each half of the board have a single color. This makes sense, but
  also suggests substantial limitation. When single-king mode is off,
  the bottom right king is predicted as a white rook.} \label{fig:allon}
\end{figure}

% % make -j eval-unblinder.exe && ./eval-unblinder.exe net.val
% .!Evaluating model net.val...
% Loaded 50000 positions in 122.59s
% Loaded model in 0.10s
% Ran eval in 2.04s
% Reading [net.val]
% net.val: 4 layers.
% net.val: num nodes: 64 1024 12288 567 837
% net.val: indices per node/fns: 49 LEAKY_RELU 36 LEAKY_RELU 127 LEAKY_RELU 78 LEAKY_RELU
% Read from net.val.
% Invert index:
% Check it:
% ModelInfo [339885 rounds, 223224128 examples]
% Over 50000 positions:
%   9584 exactly correct (19.17%)
%   161166 piece mistakes (3.22/pos)
%   1630 castling mistakes (0.03/pos)
%   19014 move mistakes (0.38/pos)
%   181810 total mistakes (3.64/pos)
% 
% % $ make -j eval-unblinder.exe && ./eval-unblinder.exe net-before-vacuum.val
% make: 'eval-unblinder.exe' is up to date.
% Evaluating model net-before-vacuum.val...
% Loaded 50000 positions in 118.80s
% Loaded model in 3.99s
% Ran eval in 332.10s
% Reading [net-before-vacuum.val]
% net-before-vacuum.val: 4 layers.
% net-before-vacuum.val: num nodes: 64 1024 12288 567 837
% net-before-vacuum.val: indices per node/fns: 64 LEAKY_RELU 1024 LEAKY_RELU 12288 LEAKY_RELU 567 LEAKY_RELU
% Read from net-before-vacuum.val.
% Invert index:
% Check it:
% ModelInfo [146999 rounds, 9407936 examples]
% Over 50000 positions:
%   10601 exactly correct (21.20%)
%   156052 piece mistakes (3.12/pos)
%   1542 castling mistakes (0.03/pos)
%   18818 move mistakes (0.38/pos)
%   176412 total mistakes (3.53/pos)
% 
% 
% 
% without concurrent processes:
% net.val: 1.61s  (something like 1035/sec/core)
% net-before-vacuum: 229.85s (something like 7/sec/core)
% 
% 
% single_kings net.val:
% Over 50000 positions:
%   9642 exactly correct (19.28%)
%   162804 piece mistakes (3.26/pos)
%   1633 castling mistakes (0.03/pos)
%   19014 move mistakes (0.38/pos)
%   183451 total mistakes (3.67/pos)
% 
% It's actually kind of heartening that it performs worse with this approach,
% though we are more likely to get the whole board correct.
% 
% (cite #kingme)
%
